Square Loss Exemplar Machine as Image Encoding: Applications on Image Retrieval

### 2016-11-07 sec_eval_raf.tex
Commenting Li et al.

\begin{table}[t]
\begin{center}
\setlength{\tabcolsep}{.2em}
\small
\begin{tabular}{l|c|ll}
\toprule
Features & dim & \textbf{Hol.} & \textbf{Ox5k} \\%& \textbf{Oxford 105k}\\
\midrule
Babenko \textit{et al.}\cite{babenko15}  & 256 & 80.2 & 58.9 \\ %& 57.8\\
Radenovi\'c \textit{et al.} \cite{RaToCh16}   & 256 & 81.5 & \un{77.4} \\
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 256 & 86.0 & 62.5 \\ %& - \\
Kalantidis  \textit{et al.} \cite{KaMeOs16}   & 256 & 83.1 & 65.4 \\
SPoC + Linear SLEM & 256 & 82.3 & 64.1 \\
SPoC + Poly SLEM & 288 & 82.3 & 60.6 \\
SPoC + Poly SLEM & 320 & 82.4 & 60.7 \\
NetVLAD + Linear SLEM & 256 & \un{88.5} & - \\
NetVLAD + Poly SLEM & 288 & 87.7 & 65.5 \\
NetVLAD + Poly SLEM & 320 & 88.3 & 65.4 \\
\midrule
Radenovi\'c \textit{et al.} \cite{RaToCh16}   & 512 & 82.5 & 79.7 \\
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 512 & 86.7 & 65.6 \\
Kalantidis \textit{et al.} \cite{KaMeOs16}   & 512 & 84.9 & 68.2 \\
Gordo \textit{et al.} \cite{GoAlReLa16} & 512 & 89.1^{\dag} & \bf{83.1}^{\dag} \\
NetVLAD + Linear SLEM & 512 & 89.3 & 68.9 \\
NetVLAD + Poly SLEM & 544 & 89.9 & 69.0 \\
NetVLAD + Poly SLEM & 576 & \un{89.9} & 69.2 \\
\midrule
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 4096 & 88.3 & 69.1 \\
Li \textit{et al.} \cite{LiLaHa15}& - & 89.2^{\dag} & 73.7 \\
NetVLAD + Linear SLEM & 4096 & 90.9 & 72.1 \\
NetVLAD + Poly SLEM & 4128 & 91.3 & 71.2 \\
NetVLAD + Poly SLEM & 4160 & \bf{91.7} & 71.7 \\
%Zepeda \textit{et al.} \cite{ZePe15} & \underline{78.3} & - & 71.8 & - & 57.5 & - & 44.6 & - & - \\
%Babenko \textit{et al.} \cite{babenko15} & - & 81.8 & - & - & - & \textbf{65.7} & - & - & 57.8\\
\hline 
\end{tabular}
\caption{Compared results to state-of-the-art features at similar dimensions, without re-ranking or query augmentation. The results using Poly SLEM or Gaussian SLEMa dd 32 or 64 dimensions to the original feature (for $r=16$ or $r=32$, respectively). Underlined results are the best at each dimension bracket and bold results are the general best. $\dag$ indicates the previous state-of-the-art.}
\end{center}
\label{sota:results}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\setlength{\tabcolsep}{.2em}
\small
\begin{tabular}{l|c|ll}
\toprule
Features & dim & \textbf{Hol.} & \textbf{Ox5k} \\%& \textbf{Oxford 105k}\\
\midrule
Babenko \textit{et al.}\cite{babenko15}  & 256 & 80.2 & 58.9 \\ %& 57.8\\
Radenovi\'c \textit{et al.} \cite{RaToCh16}   & 256 & 81.5 & \un{77.4} \\
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 256 & 86.0 & 62.5 \\ %& - \\
Kalantidis  \textit{et al.} \cite{KaMeOs16}   & 256 & 83.1 & 65.4 \\
SPoC + Linear SLEM & 256 & 82.3 & 64.1 \\
SPoC + Poly SLEM & 288 & 82.3 & 60.6 \\
SPoC + Poly SLEM & 320 & 82.4 & 60.7 \\
NetVLAD + Linear SLEM & 256 & \un{88.5} & - \\
NetVLAD + Poly SLEM & 288 & 87.7 & 65.5 \\
NetVLAD + Poly SLEM & 320 & 88.3 & 65.4 \\
\midrule
Radenovi\'c \textit{et al.} \cite{RaToCh16}   & 512 & 82.5 & 79.7 \\
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 512 & 86.7 & 65.6 \\
Kalantidis \textit{et al.} \cite{KaMeOs16}   & 512 & 84.9 & 68.2 \\
Gordo \textit{et al.} \cite{GoAlReLa16} & 512 & 89.1^{\dag} & \bf{83.1}^{\dag} \\
NetVLAD + Linear SLEM & 512 & 89.3 & 68.9 \\
NetVLAD + Poly SLEM & 544 & 89.9 & 69.0 \\
NetVLAD + Poly SLEM & 576 & \un{89.9} & 69.2 \\
\midrule
Arandjelovi\'c \textit{et al.} \cite{Arandjelovic15}& 4096 & 88.3 & 69.1 \\
%Li \textit{et al.} \cite{LiLaHa15}& - & 89.2^{\dag} & 73.7 \\
NetVLAD + Linear SLEM & 4096 & 90.9 & 72.1 \\
NetVLAD + Poly SLEM & 4128 & 91.3 & 71.2 \\
NetVLAD + Poly SLEM & 4160 & \bf{91.7} & 71.7 \\
%Zepeda \textit{et al.} \cite{ZePe15} & \underline{78.3} & - & 71.8 & - & 57.5 & - & 44.6 & - & - \\
%Babenko \textit{et al.} \cite{babenko15} & - & 81.8 & - & - & - & \textbf{65.7} & - & - & 57.8\\
\hline 
\end{tabular}
\caption{Compared results to state-of-the-art features at similar dimensions, without re-ranking or query augmentation. The results using Poly SLEM or Gaussian SLEMa dd 32 or 64 dimensions to the original feature (for $r=16$ or $r=32$, respectively). Underlined results are the best at each dimension bracket and bold results are the general best. $\dag$ indicates the previous state-of-the-art.}
\end{center}
\label{sota:results}
\end{table}
